Abstraction and Invariance for Algebraically Indexed Types

### 2012-07-09 paper/section-monoid.tex
Remove stray equation number in the monoid section

\begin{theorem}
  \label{thm:monoid-indefinability}
  Let $m$ and $n$ be natural numbers. For all $n$-by-$m$-matricies of
  natural numbers $A$ and $m$-by-$1$ matricies of natural numbers $b$,
  there exists an $M$ in the quantifier-free fragment, with
  \begin{equation}
    i_1,\dots,i_m\mathord:\mathsf{M}; \Gamma_\Mon \vdash M : \tyPrim{M}{e_1} \to \dots \to \tyPrim{M}{e_n} \to \tyPrim{M}{e}
  \end{equation}
  where $e_j = i_1^{A_{j1}}\dots i_m^{A_{jm}}$ and $e = i_1^{b_1}\dots
  i_m^{b_m}$ iff there is a solution $\vec{x} = (x_1,...,x_n)$ in the
  natural numbers to $A x^\top = b$.
\end{theorem}

>>>>

\begin{theorem}
  \label{thm:monoid-indefinability}
  Let $m$ and $n$ be natural numbers. For all $n$-by-$m$-matricies of
  natural numbers $A$ and $m$-by-$1$ matricies of natural numbers $b$,
  there exists an $M$ in the quantifier-free fragment, with
  \begin{displaymath}
    i_1,\dots,i_m\mathord:\mathsf{M}; \Gamma_\Mon \vdash M : \tyPrim{M}{e_1} \to \dots \to \tyPrim{M}{e_n} \to \tyPrim{M}{e}
  \end{displaymath}
  where $e_j = i_1^{A_{j1}}\dots i_m^{A_{jm}}$ and $e = i_1^{b_1}\dots
  i_m^{b_m}$ iff there is a solution $\vec{x} = (x_1,...,x_n)$ in the
  natural numbers to $A x^\top = b$.
\end{theorem}
